### 2016-07-21 R/ITHIM.Rmd
Install from local package, not GitHub

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
```

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install("~/ITHIM/")
#install_github("syounkin/ITHIM")
library("ITHIM")
```

@@

```{r newMETs, echo = FALSE}
newMETsFile <- "~/GHI/data/ATUS_to_METS_key.csv"
newMETs <- read.csv(file = newMETsFile, stringsAsFactors = FALSE, colClasses = c("character","character","character","character","numeric","character","character","character"))
dataColumns <- c(1,5)
D <- newMETs[,dataColumns]
metaData <- newMETs[,-dataColumns]
newMETs <- list(Data = D, metaData = metaData)
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))

rownames(newMETs$Data) <- activityCode
rownames(newMETs$metaData) <- activityCode

newMETs$metaData <- within(newMETs$metaData, {
  Travel.related..Y.N. <- as.factor(Travel.related..Y.N.)
})

metKey <- newMETs$Data$AinsworthMETS
names(metKey) <- activityCode

@@

```{r readnewMETs, echo = FALSE}
cpsFile <- "~/GHI/data/atuscps_0311.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

summaryList$metaData <- within(summaryList$metaData,{
    TESEX <- as.factor(ifelse(TESEX == 1, "male", ifelse(TESEX == 2, "female",NA)))
    AGECAT <- ifelse(TEAGE <5, "00-04",
                     ifelse(TEAGE > 4 & TEAGE < 15, "05-14",
                     ifelse(TEAGE > 14 & TEAGE < 30, "15-29",
                     ifelse(TEAGE > 29 & TEAGE < 45, "30-44",
                     ifelse(TEAGE > 44 & TEAGE < 60, "45-59",
                     ifelse(TEAGE > 59 & TEAGE < 70, "60-69",
                     ifelse(TEAGE > 69 & TEAGE < 80, "70-79", "80+"
                            )))))))})

We shift the MET estimates by the minimum value so that the new minimum MET estimate is zero.

```{r metKey, echo = FALSE}
allActivities <- colnames(summaryList$Data)
nonTravelActivities <- rownames(newMETs$metaData)[which(newMETs$metaData$Travel.related..Y.N. == "N")]
nonTravelActivities <- nonTravelActivities[which(nonTravelActivities %in% allActivities)]

activities <- nonTravelActivities

metKeyVector <- (metKey[activities] - min(metKey, na.rm = TRUE))/60*7
names(metKeyVector) <- activities
metKeyMatrix <- matrix(metKeyVector, nrow = nrow(summaryList$Data), ncol = length(metKeyVector), byrow = TRUE)
dimnames(metKeyMatrix) <- list( NULL, activities)

METs <- data.frame(METs = rowSums(summaryList$Data[,activities] * metKeyMatrix[,activities], na.rm = TRUE), AGE = summaryList$metaData$TEAGE, SEX = summaryList$metaData$TESEX, AGECAT = summaryList$metaData$AGECAT, row.names = summaryList$metaData$TUCASEID )

D <- merge(cps, METs, by.y = "row.names", by.x = "TUCASEID")
ggplot(D, aes(x = METs, ..density.., colour = AGECAT)) + geom_freqpoly(binwidth = 10) + facet_grid( SEX ~ .) + labs(x = "Non-Travel Marginal MET-hrs./week", colour = "Age") + coord_cartesian(xlim = c(0, 400))

METmatrix <- rbind(matrix(0,nrow = 2, ncol = 2), matrix(parameters$mean, ncol = 2))
METmatrix <- METmatrix/METmatrix[3,2]
```

@@

```{r total, eval = FALSE, echo = FALSE}
foo <- mapply(getTotalDistribution,
  muTravel = matrix(35,nrow = 8, ncol = 2),
  cvTravel = 1.72,
  muNonTravel = matrix(100,nrow = 8, ncol = 2),
  cvNonTravel = 1,
  p = 1,
  pWalk = rep(54.4/64.2,2),
  vWalk = rep(2.88,2),
  size = 1e5, SIMPLIFY = FALSE)
```

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
#install_github("syounkin/ITHIM", ref="devel")
install("~/ITHIM/")
library("ITHIM")
```

@@

```{r newMETs}
newMETsFile <- "~/GHI/data/ATUS_to_METS_key.csv"
newMETs <- read.csv(file = newMETsFile, stringsAsFactors = FALSE, colClasses = c("character","character","character","character","numeric","character","character","character"))
dataColumns <- c(1,5)
D <- newMETs[,dataColumns]
metaData <- newMETs[,-dataColumns]
newMETs <- list(Data = D, metaData = metaData)
```

```{r readnewMETs}
cpsFile <- "~/GHI/data/atuscps_0311.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

summaryList$metaData <- within(summaryList$metaData,{
    TESEX <- as.factor(TESEX)
    AGECAT <- ifelse(TEAGE <5, "age0-4",
                     ifelse(TEAGE > 4 & TEAGE < 15, "age5-14",
                     ifelse(TEAGE > 14 & TEAGE < 30, "age15-29",
                     ifelse(TEAGE > 29 & TEAGE < 45, "age30-44",
                     ifelse(TEAGE > 44 & TEAGE < 60, "age45-59",
                     ifelse(TEAGE > 59 & TEAGE < 70, "age60-69",
                     ifelse(TEAGE > 69 & TEAGE < 80, "age70-79", "age80+"
                            )))))))})

activities <- colnames(summaryList$Data)
metKey <- newMETs$Data$AinsworthMETS
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))
names(metKey) <- activityCode
rownames(newMETs$metaData) <- activityCode
```

```{r metKey}
metKeyVector <- (metKey[activities] - min(metKey, na.rm = TRUE))/60*7
names(metKeyVector) <- activities
metKeyMatrix <- matrix(metKeyVector, nrow = nrow(summaryList$Data), ncol = length(metKeyVector), byrow = TRUE)

METs <- data.frame(METs = rowSums(summaryList$Data * metKeyMatrix, na.rm = TRUE), AGE = summaryList$metaData$TEAGE, SEX = summaryList$metaData$TESEX, AGECAT = summaryList$metaData$AGECAT, row.names = summaryList$metaData$TUCASEID)

D <- merge(cps, METs, by.y = "row.names", by.x = "TUCASEID")
ggplot(D, aes(x = METs, ..density.., colour = AGECAT)) + geom_freqpoly() + facet_grid( SEX ~ .)
#ggplot(D, aes(x = METs, ..density.., colour = SEX)) + geom_freqpoly()
```

METmatrix <- rbind(matrix(0,nrow = 2, ncol = 2), matrix(parameters$mean, ncol = 2))
METmatrix <- METmatrix/METmatrix[3,2]

@@

@@

```{r total, eval = FALSE, echo = FALSE}
foo <- mapply(getTotalDistribution, muTravel = rep(37,2), cvTravel = rep(1.72,2), muNonTravel = rep(10,2), cvNonTravel = rep(1,2), p = rep(0.5,2), pWalk = rep(54.4/64.2,2), vWalk = rep(2.88,2), size = 1e4, SIMPLIFY = FALSE)
```
